---
title: "Wrangling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
dogs<-  read.csv("C:\\Users\\hp\\Desktop\\udacity\\wrangling\\project\\final_dataset.csv")

```

The csv file is read into a dataframe called 'dogs' in R environment . This dataset will be used to perform analysis and find insights from the given data . 
<br> 
<br>

### Distribution :


```{r}
library(ggplot2)
ggplot(data = subset(dogs , ! is.na(growth_stage )) , aes( x= growth_stage )) + geom_bar( fill = 'red')


```
<br>
From the dogs whose growth stage is knowm maximum are pupper in our dataset .

### How are retweet counts and dog growth stage  connected ? 


```{r}
library(ggplot2)

by(dogs$retweet_count , dogs$growth_stage , summary)
ggplot(data = subset(dogs , ! is.na(growth_stage )) , aes( x= growth_stage , y = retweet_count)) + geom_boxplot() + coord_cartesian(ylim = c(0,20000))
```
<br>
It found that the puppo has a high median count of retweets but the highest retweet count is of a doggo . <br>

### Favourite counts and dog stage connected ? 
```{r}
ggplot(data = subset(dogs , ! is.na(growth_stage )) , aes( x= growth_stage , y = favorite_count)) + geom_boxplot()+coord_cartesian(ylim = c(0,70000))

by(dogs$favorite_count , dogs$growth_stage , summary)

```

<br> 
puppo has the highest median favourite counts as well as the highest favourite count for a tweet .

<br> 
### Distribution of dogs based on breeds? 

<br> 
We are assuming that the first predicition p1 is the breed of the dog 

```{r}
only_dogs <- subset(dogs , dogs$p1_dog == 'True')
summary(only_dogs$p1)
```
<br>
Maximum dogs in the dataset could be golden retriever . 

`

 
